Mapping Microblog Posts to Encyclopedia Articles

### 2011-03-03 trunk/lids/twittersearchwrap/paper/paper.tex

Trending topics are listed in Table \ref{tbl:terms}.

\begin{table}[ht*]
\centering
\begin{tabular}{ c }
Search term                    \\
\hline
\#s21 \\
Karlsruhe\\
\end{tabular}
\caption{Search terms}\label{tbl:terms}
\end{table}

@@

The goal of our evaluation was to examine the stability of the entity annotations over time. To achieve this, we have repeatedly executed the same set of queries. \myremark{TODO}{How frequently? How long? Which queries?}
In a first step we have filtered the result sets such that each set is disjoint to all the other sets for the same query with respect to the messages it contains. We have then evaluated the results with respect to several measures:

>>>>

Topics trending worldwide and in Germany at Twitter retrieved on February 24th
17:20h (GMT) are listed in Table \ref{tbl:terms}. These trending topics will
constitute a basis of input search terms for our evaluation of the Twitter
Search Wrapper.

\begin{table}[ht*]
\centering
\begin{tabular}{ |l|l| }
\hline
\textsc{Trending Topic} & \textsc{Location}  \\
\hline
\#goodlucknickj & Worldwide \\
\#smalljoys & Worldwide \\
\#thingsthedevilinvented & Worldwide \\
Adam Wainwright & Worldwide \\
CatchPetrovaFire & Worldwide \\
Gadafi & Worldwide \\
Libia & Worldwide \\
Precious Minaj & Worldwide \\
Tommy John & Worldwide \\
\hline
\#gaddafi & Germany \\
\#guttenberg & Germany \\
\#libya & Germany \\
Doktorarbeit & Germany \\
Gef\"{u}hl & Germany \\
Lion & Germany \\
MBP & Germany \\
Thunderbolt & Germany \\
Vorratsdatenspeicherung & Germany \\
\hline
\end{tabular}
\caption{Search terms}\label{tbl:terms}
\end{table}

@@

The goal of our evaluation was to examine the stability of the entity
annotations over time. To achieve this, we have repeatedly executed the same set
of queries and saved the returned data. Two methods for this data acquisition
were identified: \begin{definition}[Data Acquisition Methods]
\begin{itemize}
\item Temporal Sliding Window: The query is executed and the n most
recent results are retrieved every t minutes. The Temporal Sliding Window method
may lead to duplicate messages in the retrieved documents, but needs to handle much less data and
allows for an analysis over larger time frames.
\item k-item Sliding Window: The k-item Sliding Window methods retrieves all
messages that match the query exactly one time. Each time k new messages are
available matching the given query a document containing those k messages
is retrieved. This method can lead to high data volume and needs constant
monitoring of recently posted messages matching the search term.
\end{itemize}
\end{definition}

Using the retrieved trending topics given in Table \ref{tbl:terms}
as input queries for the evaluation, the set of queries was executed twice
per hour using the Temporal Sliding Window method for data acquisition in a 24
hour time frame starting from the moment the topics were identified as trending topics.  We have then evaluated the results with respect to several measures:
